Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-13 icse/paper.tex
++
Stuff

\section{CloneRefactor}
The tool: Detect Clones, Map Context, Refactor.

@@

\subsection{Context Mapping}
\subsubsection{Relation}
\subsubsection{Location}
\subsubsection{Contents}

>>>>

\section{CloneRefactor}
% NEED TO EXPLAIN WHY DO CURRENT DETECTION TOOLS NOT SUFFICE
The tool: Detect Clones, Map Context, Refactor.

@@

\subsection{Context Mapping}
\subsubsection{Relation}
The rationale for our categories regarding clone relations.

\subsubsection{Location}
The rationale for our categories regarding clone locations.

\subsubsection{Contents}
The rationale for our categories regarding clone contents.
